---
title: "Cytoverse Test"
author: <YOUR NAME HERE>
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load cytoverse packages

```{r packages}
library(flowCore)
library(flowWorkspace)
library(openCyto)
library(ggcyto)
```

## Construct an R object (`flowSet`) from FCS files

- Hint: https://www.bioconductor.org/packages/release/bioc/vignettes/flowCore/inst/doc/HowTo-flowCore.pdf

```{r flowset}
data_path <- system.file("extdata", package = "flowWorkspaceData")
files <- list.files(pattern = "CytoTrol", path = data_path, full = TRUE)

fs <- flowCore::<YOUR FUNCTION HERE>(files = files)
fs
```

## Take a look at the first sample - can you tell how many cells there are?

```{r explore}
<YOUR CODE HERE>
```

## Determine which cytometer was used from the FCS keywords.

- Hint: "$CYT" denotes the type of flow cytometer.

```{r cytometer}
<YOUR CODE HERE>
```

## Compensation

Before proceeding with further analysis of the data in flowSet, it is important to properly compensate the data for spectral overlap between fluorescence channels.

```{r compensation}
compensation_matrix <- flowCore::fsApply(fs, function(x) flowCore::spillover(x)[[1]], simplify = FALSE)
fs_compensated <- flowCore::<YOUR FUNCTION HERE>(fs, compensation_matrix)
```

## Transformation

All of the stained channels need to be transformed properly before the gating. Here we use the `flowCore::estimateLogicle` method to determine the logicle transformation.

```{r transformation}
transList <- flowCore::estimateLogicle(fs_compensated[[1]], names(markernames(fs)))
fs_transformed <- flowCore::<YOUR FUNCTION HERE>(fs_compensated, transList)
```

## Visualize the expression values of CD8 (`CD8 APCH7`) from original flowSet, compensated flowSet, and transformed flowSet

- Hint: https://www.bioconductor.org/packages/release/bioc/vignettes/ggcyto/inst/doc/autoplot.html

```{r plot}
<YOUR CODE HERE>
```

## Compute the median expression values for each channel in the first sample

- Hint: https://www.bioconductor.org/packages/release/bioc/vignettes/flowCore/inst/doc/HowTo-flowCore.pdf

```{r median}
<YOUR CODE HERE>
```

## Create a gating set object from `fs_transformed`

```{r create-gs}
gs <- flowWorkspace::<YOUR FUNCTION HERE>(fs_transformed)
```

## Load the gating template

- Hint: https://www.bioconductor.org/packages/release/bioc/manuals/openCyto/man/openCyto.pdf

```{r template}
gtFile <- system.file("extdata/gating_template/tcell.csv", package = "openCyto")
gt <- openCyto::<YOUR FUNCTION HERE>(gtFile)
gt
```

## Plot the gating template

```{r plot-template}
plot(gt)
```

## Apply the gating template to the gating set

```{r gating}
openCyto::<YOUR FUNCTION HERE>(gt, gs)
```

## Plot the gates of the first sample

- Hint: https://www.bioconductor.org/packages/release/bioc/vignettes/ggcyto/inst/doc/autoplot.html

```{r first-plot}
ggcyto::autoplot(gs[[1]])
```

## Plot the lymphocyte gate (`lymph`) of all samples

- Hint: https://www.bioconductor.org/packages/release/bioc/vignettes/ggcyto/inst/doc/autoplot.html

```{r lymph-plot}
<YOUR CODE HERE>
```

## Retrieve the cell populations from the gating set object

- Hint: https://www.bioconductor.org/packages/release/bioc/vignettes/flowWorkspace/inst/doc/flowWorkspace-Introduction.html

```{r pops}
flowWorkspace::<YOUR FUNCTION HERE>(gs)
```

Questions to check understanding:
```{r, questions}
# 1. What are the marker names used in these FCS files?

# 2. How many different cell populations (nodes) are defined in the gating template?

# 3. How many CD4+ T cells and CD8+ T cells are in each sample?

# 4. Looking at the density plots of CD8 marker expression after transformation in the report, where would you put a partition line to divide the low and high expressed cells? Note: Expression is on the x-axis. Also, how would you do it programatically?
  
  
```
